---
title: "432 Lab 2 Template (replace these words)"
subtitle: "Use your own subtitle, if you like."
author: "Your Name Goes Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: zephyr  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor)
library(naniar)
library(readxl) # needed here to ingest the data from an Excel sheet

# load other packages as desired

library(easystats)
library(tidyverse) # load tidyverse last

theme_set(theme_bw()) # set theme for ggplots
```

## Loading the Data {.unnumbered}

::: {.callout-note}

After downloading the `hbp_3024.xlsx` file to your computer, you should ingest the data using `read_xlsx()` from the `readxl` package. Be sure to handle the missingness properly.

Note that the resulting tibble should have 3024 rows and 23 columns, and you should see missing data on 8 of the 23 variables, including for example, LDL cholesterol.

Delete this note and all other instructions from this template before submitting your work.

:::


# Question 1

## Part A

::: {.callout-note}
Follow the instructions, and remove this line from your final submission.
:::

## Part B

::: {.callout-note}
Follow the instructions, and remove this line from your final submission.
:::

## Part C

::: {.callout-note}
Follow the instructions, and remove this line from your final submission.
:::

# Question 2

## Part A

::: {.callout-note}
Follow the instructions, and remove this line from your final submission.
:::

## Part B

::: {.callout-note}
Follow the instructions, and remove this line from your final submission.
:::

## Part C

::: {.callout-note}
Follow the instructions, and remove this line from your final submission.
:::

# AI Usage

The most common response here would be:

> I used no AI here, other than code completion and spell-checking in RStudio.

::: {.callout-note}
Please provide additional information about other AI tools you used. If the statement above applies to you, format this section properly to include only that statement, without the ">" at the beginning.
:::

# Session Information

```{r}
xfun::session_info()
```
