---
title: "Project A Template for 432 in Spring 2026"
subtitle: "Insert Your Subtitle Here (No More than 120 characters)"
author: "Your Name and Your Partner's Name"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: zephyr  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor) 
library(naniar)

# load other packages as desired

library(easystats)
library(tidyverse) # load tidyverse last

theme_set(theme_bw()) # set theme for ggplots
```

# Data Source

Follow the Project A instructions.

# The Subjects

Follow the Project A instructions.

# Loading and Tidying the Data

## Loading the Raw Data

Follow the Project A instructions.

## Cleaning the Data

Follow the Project A instructions, using the subsections below that are necessary, and eliminating the others.

### Selecting Variables We'll Use

### Changing Variable Names

### Sampling the Data

### Converting Variable Types

### Working with Categorical Predictors

### Arranging the Tibble

# The Tidy Tibble

Follow the Project A instructions.

## Listing the Tibble

## Size and Identifiers

## Saving as an Rds file

# The Code Book

## Five Key Statements

Follow the Project A instructions. See the [Project A Demonstration](https://thomaselove.github.io/432-2026/432_projectA_demo.html) for an example.

## Describing the Variables

Variables included in the `nh_demo` data are summarized and described in five different ways in the panel below. Click on the tab that interests you to see results. 

:::{.callout-tip}

Please provide, at minimum, the variable descriptions list and the data_codebook() results here. You can include the others if you like.

:::

::: {.panel-tabset}

### Definitions

Provide definitions of your variables in a table here. See the [Project A Demonstration](https://thomaselove.github.io/432-2026/432_projectA_demo.html) for a more detailed example.

### `data_codebook()`

Provide `data_codebook()` results for your tibble here.

```{r}
data_codebook(nh_demo)
```

### Other Tabs (optional)

Add other tabs here if you like with things like `describe()`, `tbl_summary()` or Missingness information. See the [Project A Demonstration](https://thomaselove.github.io/432-2026/432_projectA_demo.html) for a detailed example.

:::


# Linear Regression Design

Follow the Project A instructions.

## My First Research Question

## My Quantitative Outcome

### Numerical Summary of my linear outcome

```{r}
#| eval: false # note that you'll need to remove this line completely

Hmisc::describe(yourdatasetname$youroutcomenamegoeshere)

mosaic::favstats(yourdatasetname$youroutcomenamegoeshere)

yourdatasetname |> tabyl(youroutcomenamegoeshere) |> adorn_pct_formatting() |>
  arrange(desc(n)) |> head(5)
```

### Summary Statements about my outcome, insertyouroutcomenamehere

My outcome is insertnamehere.

- I have XXX observations and no missing values on insertnamehere.
- I have XXX distinct values of insertnamehere.
- The range is XX to XX, with mean XX and standard deviation XX insertunitshere.
- The most common value for insertnamehere is XX, which occurs in XX% of my subjects. 

## Linear Model Predictor Candidates

Follow the Project A instructions.

### Anticipated Direction of Effects

### Missingness Summary

```{r}
#| eval: false  # you'll have to drop this line

linear_model_predictors <- insertdetailshere

miss_var_summary(linear_model_predictors) |> filter(n_miss > 0)
miss_case_table(linear_model_predictors)
```

- I have complete data for all of the linear model predictors in XX (XX%) of the XX rows in my data.
- I am missing XX values (XX%) for insertvariablenamehere.

# Logistic Regression Design

Follow the Project A instructions.

## My Second Research Question

## My Binary Outcome

## Logistic Model Predictor Candidates

### Anticipated Direction of Effects

### Missingness Summary

```{r}
#| eval: false  # you'll have to drop this line

logistic_model_predictors <- insertdetailshere

miss_var_summary(logistic_model_predictors) |> filter(n_miss > 0)
miss_case_table(logistic_model_predictors)
```

- I have complete data for all of the logistic model predictors in XX (XX%) of the XX rows in my data.
- I am missing XX values (XX%) for insertvariablenamehere.

# Linear Regression Analyses

Follow the Project A instructions.

## Missingness

## Outcome Transformation

## Scatterplot Matrix and Collinearity

## Model A

### Fitting Model A

### Tidied Coefficient Estimates (Model A)

### Summarizing Fit (Model A)

### Regression Diagnostics (Model A)

```{r}
#| fig-height: 8

# check_model(modelA)
```

## Non-Linearity

## Model B

### Fitting Model B

### Tidied Coefficient Estimates (Model B)

### Effects Plot for Model B

### Summarizing Fit (Model B)

### Regression Diagnostics (Model B)

## Validating Models A and B

### Validated $R^2$ statistics

Model | Validated $R^2$
-----: | --------
A | 
B | 

## Final Linear Regression Model

I prefer Model `XX`, because ...

### Winning Model's Parameter Estimates

### Effects Plot for Winning Model

### Numerical Description of Effect Sizes

### Nomogram of Winning Model

### Prediction for a New Subject

# Logistic Regression Analyses

Follow the Project A instructions.

## Missingness

## Model Y

### Fitting Model Y

### Tidied Odds Ratio Estimates (Model Y)

### Effects Plot (Model Y)

### Summarizing Fit (Model Y)

### Confusion Matrix (Model Y)

My prediction rule is ...


## Non-Linearity

## Model Z

### Fitting Model Z

### Tidied Odds Ratio Estimates (Model Z)

### Effects Plot (Model Z)

### Summarizing Fit (Model Z)

### Confusion Matrix (Model Z)

As in Model Y, my prediction rule is ...

## Validating Models Y and Z

### Validated $R^2$ and $C$ statistics for each model

## Final Logistic Regression Model

I prefer Model `XX`, because ...

### Winning Model's Parameter Estimates

### Plot of Effect Sizes for Winning Model

### Numerical Description of Effect Sizes

### Plot of ROC Curve for Winning Model

### Validated $R^2$ and $C$ statistic for Winning Model

### Nomogram of Winning Model

### Predictions for Two New Subjects

# Discusssion

Follow the Project A instructions.

## Answering My Research Questions 

## Thoughts on Project A

# Affirmation

Follow the Project A instructions. The text we want to see here is

> I am certain that it is completely appropriate for these data to be shared with anyone, without any conditions. There are no concerns about privacy or security.

# References

1. Data Source description
2. Others, as needed.

# Use of AI

Follow the Project A instructions.

# Session Information

```{r}
xfun::session_info()
```
