---
title: "432 Lab 3 Template (replace these words)"
subtitle: "Use your own subtitle, if you like."
author: "Your Name Goes Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: united  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor)
library(naniar)
library(rms)

# load other packages as desired

library(easystats)
library(tidyverse) # load tidyverse last

theme_set(theme_lucid()) # set theme for ggplots
```

## Loading the Data {.unnumbered}

::: {.callout-note}
Delete this note and all other instructions from this template before submitting your work. The `nh_1500` data should have 1500 rows (subjects) and 30 columns (variables.)
:::


# Question 1

## Part A

## Part B

## Part C

# Question 2

## Part A

## Part B

## Part C

# AI Usage

The most common response here would be:

> I used no AI here, other than code completion and spell-checking in RStudio.

::: {.callout-note}
Please provide additional information about other AI tools you used. If the statement above applies to you, format this section properly to include only that statement, without the ">" at the beginning.
:::

# Session Information

```{r}
xfun::session_info()
```
