---
title: "432 Project A Plan Template"
subtitle: "Here's a place for a subtitle"
author: "Your Name (and Your Partner's Name) Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: spacelab  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor) 
library(naniar)

# load other packages as desired here

library(easystats)
library(tidyverse) # load tidyverse last

theme_set(theme_bw()) # set theme for ggplots
```

# Data Source

Follow the Project A instructions.

# The Subjects

Follow the Project A instructions.

# Loading and Tidying the Data

## Loading the Raw Data

Follow the Project A instructions.

## Cleaning the Data

Follow the Project A instructions, using the subsections below that are necessary, and eliminating the others.

### Selecting Variables We'll Use

### Changing Variable Names

### Sampling the Data

### Converting Variable Types

### Working with Categorical Predictors

### Arranging the Tibble

# The Tidy Tibble

Follow the Project A instructions.

## Listing the Tibble

## Size and Identifiers

## Save The Tibble

# The Code Book

## Defining the Variables

## Numerical Description

# Linear Regression Plans

Follow the Project A instructions.

## My First Research Question

## My Quantitative Outcome

### Numerical Summary of my linear outcome

```{r}
#| eval: false # note that you'll need to remove this line completely

Hmisc::describe(yourdatasetname$youroutcomenamegoeshere)

mosaic::favstats(yourdatasetname$youroutcomenamegoeshere)

yourdatasetname |> tabyl(youroutcomenamegoeshere) |> adorn_pct_formatting() |>
  arrange(desc(n)) |> head(5)
```

### Summary Statements about my outcome, insertyouroutcomenamehere

My outcome is insertnamehere.

- I have XXX observations and no missing values on insertnamehere.
- I have XXX distinct values of insertnamehere.
- The range is XX to XX, with mean XX and standard deviation XX insertunitshere.
- The most common value for insertnamehere is XX, which occurs in XX% of my subjects. 

## My Planned Predictors (Linear Model)

### Anticipated Direction of Effects

### Missingness Summary

```{r}
#| eval: false  # you'll have to drop this line

linear_model_predictors <- insertdetailshere

miss_var_summary(linear_model_predictors) |> filter(n_miss > 0)
miss_case_table(linear_model_predictors)
```

- I have complete data for all of the linear model predictors in XX (XX%) of the XX rows in my data.
- I am missing XX values (XX%) for insertvariablenamehere.

# Logistic Regression Plans

Follow the Project A instructions.

## My Second Research Question

## My Binary Outcome

## My Planned Predictors (Logistic Model)

### Anticipated Direction of Effects

### Missingness Summary

```{r}
#| eval: false  # you'll have to drop this line

logistic_model_predictors <- insertdetailshere

miss_var_summary(logistic_model_predictors) |> filter(n_miss > 0)
miss_case_table(logistic_model_predictors)
```

- I have complete data for all of the logistic model predictors in XX (XX%) of the XX rows in my data.
- I am missing XX values (XX%) for insertvariablenamehere.


# Affirmation

Follow the Project A instructions. The text we want to see here is

> I am certain that it is completely appropriate for these data to be shared with anyone, without any conditions. There are no concerns about privacy or security.

# References

1. Data Source description
2. Others, as needed.

# Session Information

```{r}
xfun::session_info()
```
