---
title: "432 Lab 1 Template (replace these words)"
subtitle: "Use your own subtitle, if you like."
author: "Your Name Goes Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: default  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor)
library(naniar)

# load other packages as desired

library(easystats)
library(tidyverse) # load tidyverse last

theme_set(theme_bw()) # set theme for ggplots
```

## Loading the Data {.unnumbered}

```{r}
chr2024 <- 
  read_csv("https://raw.githubusercontent.com/THOMASELOVE/432-data/refs/heads/master/data/chr_2024.csv", show_col_types = FALSE) 

dim(chr2024)
```

Note that we should have 3054 rows and 30 columns here.

## Creating the Ohio sample {.unnumbered}

```{r}
ohio24 <- chr2024 |> filter(state == "OH")

dim(ohio24)
```


# Question 1

## Part A

Follow the instructions, and remove this line from your final submission.

## Part B

# Question 2

## Part A

Follow the instructions, and remove this line from your final submission.

### Fitting `model1`

```{r}
model1 <- lm(obesity ~ 1, data = ohio24) # obviously needs correction
```

## Part B

### Checking Regression Assumptions for `model1`

```{r}
#| fig-height: 8

check_model(model1)
```

## Part C

### Comparing `model1` to `model2`

# Session Information

```{r}
xfun::session_info()
```
