---
title: "Project B Template for 432 in Spring 2026"
subtitle: "Insert Your Subtitle Here (No More than 120 characters)"
author: "Your Name and Your Partner's Name"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: pulse  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor) 
library(naniar)
library(conflicted) 

# load other packages as desired

library(easystats)
library(tidyverse) # load tidyverse last

theme_set(theme_lucid()) # set theme for ggplots
```

# Background

# Research Questions

# Data Ingest and Management

## Loading the Raw Data

## Cleaning the Data

Use or edit the subsections below that are helpful and drop the rest.

### Selecting Variables We'll Use

### Changing Variable Names

### Sampling the Data

### Converting Variable Types

### Working with Categorical Predictors

### Arranging the Tibble

## Print and Save The Final Tibble

# Code Book and Description

## Defining the Variables

## Numerical Description

# Analysis 1

## Managing Data for Analysis 1

## Outcome and Predictor Details

## Regression Modeling

## Further Details

# Analysis 2

## Managing Data for Analysis 2

## Outcome and Predictor Details

## Regression Modeling

## Further Details

# Conclusions and Discussion

## Answering My Research Questions 

# References and Acknowledgments

## References

1. Data Source description
2. Others, as needed.

## Acknowledgments

Thank anyone you should thank.

# Use of AI

Follow the same advice as the Project A instructions.

# Session Information

```{r}
xfun::session_info()
```
