---
title: "432 Lab 1 Template (replace these words)"
subtitle: "Use your own subtitle, if you like."
author: "Your Name Goes Here"
date: "`r Sys.Date()`"
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    theme: default  ## change the theme if you prefer
---

## R Packages and Setup

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor) # load other packages as desired

library(tidyverse) # load tidyverse last

theme_set(theme_bw()) # set theme for ggplots
```

## Loading the Data

```{r}
oh22 <- 
  read_csv("https://raw.githubusercontent.com/THOMASELOVE/432-data/master/data/oh_counties_2022.csv", show_col_types = FALSE) |>
  clean_names() |>
  mutate(fips = as.character(fips))

dim(oh22)
```

Note that we should have 88 rows and 43 columns here.

# Question 1

Follow the instructions, and remove this line from your final submission.

# Question 2

Follow the instructions, and remove this line from your final submission.

## Fitting `model1`

```{r}
model1 <- lm(obese_pct ~ 1, data = oh22) # obviously needs correction
```


## Explaining the `food_env` coefficient

## Checking Regression Assumptions for `model1`

```{r}
#| fig-height: 8

par(mfrow=c(2,2)); plot(model1); par(mfrow = c(1,1))
```


## Comparing `model1` to `model2`

# Session Information

```{r}
xfun::session_info()
```
