---
title: "432 Project B Portfolio Template"
subtitle: "Here's a place for a subtitle if you use one"
author: "Your Name (and Your Partner's Name) Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: zephyr  ## change the theme if you prefer
---

## R Packages and Setup {.unnumbered}

```{r}
#| message: false
#| warning: false

knitr::opts_chunk$set(comment = NA) # do not remove this

library(janitor) # load other packages as desired

library(tidyverse) # load tidyverse last

theme_set(theme_bw()) # set theme for ggplots
```

# Background

# Research Questions

# Data Ingest and Management

## Loading the Raw Data

## Cleaning the Data

Use or edit the subsections below that are helpful and drop the rest.

### Selecting Variables We'll Use

### Changing Variable Names

### Sampling the Data

### Converting Variable Types

### Working with Categorical Predictors

### Arranging the Tibble

## Print and Save The Final Tibble

# Code Book and Description

## Defining the Variables

## Numerical Description

# Analyses

## Analysis 1

## Analysis 2

# Conclusions and Discussion

## Answering My Research Questions 

# References and Acknowledgments

## References

1. Data Source description
2. Others, as needed.

## Acknowledgments

Thank anyone you should thank.

# Session Information

```{r}
xfun::session_info()
```
